Simple repression draft

### 2020-09-24 doc/resubmission/appendix_02_bursty.tex
updates before bringing back Dropbox documents

\begin{figure}[h!]
\centering
\includegraphics{../figures/si/figS0X_bursty_states.pdf}
\caption{
\textbf{Bursty transcription for unregulated promoter.}
(A) Schematic of the one-state bursty transcription model. Rate $k_i$ is the
bursty initiation rate, $\gamma$ is the mRNA degradation rate, and $b$ is the
mean burst size. (B) Schematic depiction of the mRNA count state transitions.
The model in (A) allows for transitions of $> 1$ mRNA counts with probability
$G_{m-m'}$, where the state jumps from having $m'$ mRNA to having $m$ mRNA in a
single burst of gene expression.}
\label{figS1:bursty_one_state}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=5cm]{../figures/si/figS0X_reindex_sum.pdf}
\caption{\textbf{Reindexing double sum.} Schematic for reindexing the sum
$\sum_{m=0}^\infty \sum_{m'=0}^m$. Blue circles depict the 2D grid of
nonnegative integers restricted to the lower triangular part of the $m, m'$
plane. The trick is that this double sum runs over all $(m, m')$ pairs with
$m'\le m$. Summing $m$ first instead of $m'$ requires determining the
boundary: the upper boundary of the $m'$-first double sum becomes the
lower boundary of the $m$-first double sum.}
\label{figS2:sum_reindex}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../figures/si/figS0X_Shahrezaei_promoter.pdf}
\caption{\textbf{Schematic of three-stage promoter from~\cite{Shahrezaei2008}.}
Adapted from Shahrezaei \& Swain~\cite{Shahrezaei2008}. In their paper they
derive a closed form solution for the protein distribution. Our two-state bursty
promoter at the mRNA level can be mapped into their solution with some
relabeling.}
\label{fig:shahrezaei}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics{../../figures/si/figS0X_bursty_states.pdf}
\caption{
\textbf{Bursty transcription for unregulated promoter.}
(A) Schematic of the one-state bursty transcription model. Rate $k_i$ is the
bursty initiation rate, $\gamma$ is the mRNA degradation rate, and $b$ is the
mean burst size. (B) Schematic depiction of the mRNA count state transitions.
The model in (A) allows for transitions of $> 1$ mRNA counts with probability
$G_{m-m'}$, where the state jumps from having $m'$ mRNA to having $m$ mRNA in a
single burst of gene expression.}
\label{figS1:bursty_one_state}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=5cm]{../../figures/si/figS0X_reindex_sum.pdf}
\caption{\textbf{Reindexing double sum.} Schematic for reindexing the sum
$\sum_{m=0}^\infty \sum_{m'=0}^m$. Blue circles depict the 2D grid of
nonnegative integers restricted to the lower triangular part of the $m, m'$
plane. The trick is that this double sum runs over all $(m, m')$ pairs with
$m'\le m$. Summing $m$ first instead of $m'$ requires determining the
boundary: the upper boundary of the $m'$-first double sum becomes the
lower boundary of the $m$-first double sum.}
\label{figS2:sum_reindex}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{../../figures/si/figS0X_Shahrezaei_promoter.pdf}
\caption{\textbf{Schematic of three-stage promoter from~\cite{Shahrezaei2008}.}
Adapted from Shahrezaei \& Swain~\cite{Shahrezaei2008}. In their paper they
derive a closed form solution for the protein distribution. Our two-state bursty
promoter at the mRNA level can be mapped into their solution with some
relabeling.}
\label{fig:shahrezaei}
\end{figure}

### 2020-09-24 doc/resubmission/section_02_means.tex
updates before bringing back Dropbox documents

The second class of models that allow us to access the mean gene expression use
chemical master equations to compute the probabilities of the different
microscopic states ~\cite{Ko1991, Peccoud1995, Record1996, Kepler2001,
Sanchez2008, Shahrezaei2008, Sanchez2011, Michel2010}. As seen in
Figure~\ref{fig1:means_cartoons}(C), we consider a host of different
nonequilibrium models, each of which will have its own result for both the mean
(this section) and noise (next section) in gene expression.

>>>>

The second class of models that allow us to access the mean gene expression use
chemical master equations to compute the probabilities of the different
microscopic states ~\cite{Ko1991, Peccoud1995, Record1996, Kepler2001,
Sanchez2008, Shahrezaei2008, Sanchez2011, Michel2010}. The main differences
between both modeling approaches can be summarized as: 1) Although for both
classes of models the steps involving transcriptional events are assumed to be
strictly irreversible, thermodynamic models force the regulation, i.e., the
control over the expression exerted by the repressor, to be in equilibrium. This
does not need to be the case for kinetic models. 2) Thermodynamic models ignore
the mRNA count from the state of the Markov process, while kinetic models keep
track of both the promoter state and the mRNA count. 3) Finally, thermodynamic
and kinetic models coarse-grain to different degrees the molecular mechanisms
through which RNAP enters the transcriptional event. As seen in
Figure~\ref{fig1:means_cartoons}(C), we consider a host of different kinetic
models, each of which will have its own result for both the mean (this section)
and noise (next section) in gene expression.
